Mobility Boomerang Plots

### 2020-07-24 notebooks/embedding_boomerang_plots.rmd
commited the wrong notebook last time

tab <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/norm/d300_ws1_precedence_norm_by_country.csv")

@@

write_csv(tab, "~/Desktop/norm_by_country.csv")
```

>>>>

df %>%
  filter(country_iso_alpha %in% selected) %>%
  group_by(country_iso_name) %>%
  summarize(
    mu = mean(l2norm)
  ) %>%
  arrange(mu)

plotdata <- df %>%
  filter(country_iso_name != "NULL") %>%
  filter(country_iso_alpha %in% selected) %>%
  rename(country = country_iso_name) %>%
  mutate(
    country = ifelse(country == "Russian Federation", "Russia", country),
    country = ifelse(country == "Korea, Republic of", "South Korea", country),
    country = ifelse(country == "Taiwan, Province of China", "Taiwan", country),
    country = ifelse(country == "Iran, Islamic Republic of", "Iran", country),
  )

mu <- plotdata %>%
  group_by(country) %>%
  summarize(
    mu = mean(l2norm)
  )

plotdata %>%
  left_join(mu, by = "country") %>%
  ggplot(aes(l2norm, group = country)) +
  geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
  geom_vline(aes(xintercept = mu)) +
  geom_text(
    data = mu,
    aes(label = paste0("mu==", round(mu, 1))), 
    parse = T,
    x = 1.5, 
    y = 0.18, 
    size = 3
  ) +
  facet_wrap(~country) +
  scale_y_continuous(breaks = c(0, 0.2)) +
  theme_minimal() +
  theme(
      text = element_text(family = "Helvetica", size = 14),
      axis.title.x = element_text(angle = 0, size = 16, face = "bold", vjust = 0.5),
      axis.title.y = element_text(angle = 90, size = 16, face = "bold"),
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.border = element_rect(size = 0.5, color = "black", fill = NA),
  ) +
  xlab("L2 Norm of Organization Vectors by Country") +
  ylab("Proportion")

```{r}
tab <- read_csv("/Users/dakotamurray/Dropbox/SME-dropbox/Data/Derived/Embeddings/precedence/norm/d300_ws1_precedence_norm_by_country.csv")

@@

tab
write_csv(tab, "~/Desktop/norm_by_country.csv")
```
